### 2015-06-12 inst/vign/taxize_vignette.Rmd
updated readme, updated vignettes, bumped patch version

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{taxize vignette}
-->

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE
)
```

@@

```{r loadtaxize, messages=FALSE, warning=FALSE}
library("taxize")
```

@@

```{r resolvenames, eval=TRUE, cache=FALSE}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
head( temp$results )
```

@@

```{r tnrs, eval=TRUE, cache=FALSE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames, source = "iPlant_TNRS")[ , -c(5:7)]
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
(tsn <- get_tsn(mynames, accepted = FALSE))
library("plyr")
ldply(tsn, itis_acceptname)
```

@@

```{r itisclass, eval=TRUE, cache=FALSE}
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
```

@@

[eol]: http://www.eol.org/
[ncbi]: http://www.ncbi.nlm.nih.gov/
[itis]: http://www.itis.gov/
[phylomatic]: http://phylodiversity.net/phylomatic/
[opentree]: http://blog.opentreeoflife.org/
[wikispecies]: http://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/
[iucn]: http://www.iucnredlist.org/

>>>>

<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{taxize vignette}
%\VignetteEncoding{UTF-8}
-->

```{r, eval=TRUE, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  warning = FALSE,
  message = FALSE,
  cache.path = "cache/"
)
```

@@

```{r loadtaxize}
library("taxize")
```

@@

```{r resolvenames}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
head( temp$results )
```

@@

```{r tnrs, cache=TRUE}
mynames <- c("Helianthus annuus", "Pinus contort", "Poa anua", "Abis magnifica",
  	"Rosa california", "Festuca arundinace", "Sorbus occidentalos","Madia sateva")
tnrs(query = mynames, source = "iPlant_TNRS")[ , -c(5:7)]
```

@@

```{r synonyms, eval=TRUE, cache=FALSE, message=FALSE, warning=FALSE, comment=NA}
mynames <- c("Helianthus annuus ssp. jaegeri", "Helianthus annuus ssp. lenticularis", "Helianthus annuus ssp. texanus")
(tsn <- get_tsn(mynames, accepted = FALSE))
lapply(tsn, itis_acceptname)
```

@@

```{r classification}
specieslist <- c("Abies procera","Pinus contorta")
classification(specieslist, db = 'itis')
```

@@

[eol]: http://www.eol.org/
[ncbi]: http://www.ncbi.nlm.nih.gov/
[itis]: http://www.itis.gov/
[wikispecies]: http://species.wikimedia.org/wiki/Main_Page
[col]: http://www.catalogueoflife.org/
